On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-04 tt_theorem.tex
12/4 before lunch

Suppose $w[i]$ ware stabilized without any bond, that is, by a tunnel.
For that the two points that are a neighbor of both $w[i-1]$ and $w[i]$ must be occupied already.
In addition, at least one of the neighbors of $w[i]$ must be free because $S[i+1] = b$.
Thus, only the case to be considered is Fig.~\ref{TTT_tunnel_direction} (middle) with $n_5$ being occupied (that is, $n_4$ is free).
In this case, before $w[i]$ is stabilized, at lest three neighbors of $n_2$ ware free and hence, a bead at $n_2$ was provided with one free bond and could form a bond with $w[i]$. \qed

\begin{figure}
  \begin{center}
    \begin{tabular}{ccc}

@@

@@

\begin{lemma}
\label{TTT_exit}
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$ and arity $\alpha =2$.
%Let $w[i]$ be a bead which is stabilized at the exit of a tunnel.
If $S[h..i+1] = bt^{(i-h)}b$ for some $h<i-1$ and $S[i] = t_s$ or $t_o$, then $\#bc(C_{i-2}) \geq \#bc(C_i)$, and hence, $\#bc(C_{h-1}) \geq \#bc(C_i)$.
If $h < i-1$, then the second inequality is strengthened as $\#bc(C_{h-1}) > \#bc(C_{i})$.
%if we assume $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
\end{lemma}

\begin{proof}%[Lemma~ \ref{TTT_exit}]
Since the binding capability never increases inside a tunnel, we just need to consider the exit of a tunnel.
See Fig.\ref{TTT_tunnel_exit}. 
At least one of points $n_1$ or $n_2$ must be free because otherwise $w[i]$ would be inside of a tunnel, that is, $S[i+1]$ would not be $b$.

Let $a$ be the number of bonds $w[i-1]$ forms, that is, $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$. Then, $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$ as follows.

\begin{itemize}
\item{Case of both $n_1$ and $n_2$ being free}\\
  This case can be regarded the same as entrance. See Fig.\ref{TTT_tunnel_exit} (Left). Predecessor $n_5$ has to be bound to $n_4$ and $n_5$ because both of $n_3$ and $n_4$ have binding capabilities. Hence, $a \geq 2$. This time, $\alpha = 2$, that is, this case $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.

\item{Case of $n_1$ is occupied}\\
  See Fig.\ref{TTT_tunnel_exit} (Right). If $n_1$ is occupied, then $n_2$ is free so that $n_5$ has to be bound $n_4$. Hence,  $a \geq 1$. This case can supply two binding capabilities but $p^\prime$ can bind to only one of $n_0$ or $n_2$ because $n_0$ or $n_2$ will be occupied by the successor of $p^\prime$. Therefore, this case $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.

\end{itemize}

Thus,$\#bc(C_{i-2}) \geq \#bc(C_i)$ , and hence, $\#bc(C_{h-1}) \geq \#bc(C_i)$.
If $h < i-1$, then the second inequality is strengthened as $\#bc(C_{h-1}) > \#bc(C_{i})$ because $S[h] = b$, that is, $\#bc(C_{h-1}) > \#bc(C_h)$ and $\#bc(C_{h}) \geq \#bc(C_i)$. \qed

\begin{figure}
  \centering
    \begin{tabular}{cc}
    \centering
      \begin{minipage}{0.45\linewidth}
      \centering
        \begin{tikzpicture}
	\draw[white] (0:0) -- (120:1);
	\draw[white] (0:0) -- (-60:1);
	\draw[white] (0:0) -- (0:1);

            \fill[blue](0,0) circle [radius=0.05];
            \node[above] at (0,0) {$w[i]$};

@@

            \node[transform canvas={shift=(60:1)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
            \node[transform canvas={shift=(120:1)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
            \node[transform canvas={shift=(180:1)},above] {$w[i-1]$};

@@

            \fill[blue](0,0) circle [radius=0.05];
            \node[above] at (0,0) {$w[i]$};

@@

            \node[transform canvas={shift=(0:1)},right] {$n_0$};
            \node[transform canvas={shift=(60:1)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
            \node[transform canvas={shift=(120:1)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
            \node[transform canvas={shift=(180:1)},above] {$w[i-1]$};

          \node at (0,-2) {Point $n_1$ is occupied};
        \end{tikzpicture}
      \end{minipage}
    \end{tabular}
    \caption{Exit of Tunnel}
    \label{TTT_tunnel_exit}
\end{figure}
\end{proof}

@@

\begin{lemma}
\label{TTT_tunnelC_lemma}
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ and $S[i+2] = t_a$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $S[i+l+2] = t_a$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
\end{lemma}

@@

\begin{proof}[Lemma~ \ref{TTT_tunnelC_lemma}]
Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$.
Assume $S[h..i+1] = bt^{i-h}b (h<i)$. If at least one of $w[h+1..i]$ are stabilized by tunnel $C$, then only $w[h+1]$ can use tunnel $C$ because if $w[g]$ which is one of $w[h+2..i]$, with $h+2 \leq g \leq i$ is stabilized by tunnel $C$, $C_g$ is a terminal.

Let us consider stabilization $S[h-1..h+1] = tbt$ or $S[h-1..h+1] = bbt$ as follows. In result, $\#bc(C_{h-3}) > \#bc(C_{h+1})$. In addition according to Lemma~\ref{TTT_exit} $\#bc(C_{h+1}) \geq \#bc(C_{i})$. Thus, $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_{i})$.
\\

\subsubsection{Case of $S[h-1..h+1] = bbt$}
See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
If $w[h-1]$ forms one bond, then it leaves one free bond, but it is consumed by $w[h+1]$.
In addition, $w[h]$ has to bound.
Thus, in this cases, binding capability decreases by 1.
If $w[h-1]$ forms two bonds, then it does not leave any bond.
In addition, $w[h]$ has to be bound.
Thus, in this case, even if $w[h+1]$ supplies two free bonds, binding capability decreases by 1.

@@

\subsubsection{Case of $S[h-1..h+1] = tbt_a$}
Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.

%\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
  In this figure, Bead $n_4$ has at least one binding so that $w[h-1]$ has to bound $n_4$. Moreover, $w[h]$ has to bind to one of $n_1, n_2, n_3$ in order to stabilize deterministically. On the other hand, $w[h+1]$ can supply two bindings but has only two free neighbors. One of them is occupied by a successor. Therefore $w[h+1]$ can only bind one of $n_5, n_6$, that is, $w[h+1]$ supplies at most one binding. Thus, this case $\#bc(C_{h-1}) > \#bc(C_{h+1})$.

  These cases are divided on number of capabilities that $w[h-1]$ consumes.
  \begin{itemize}
  \item[-]{$w[h-1]$ does not consume any bindings}\\
  According to Lemma~\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
    $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically so that  $\#bc(C_{h-1}) > \#bc(C_{h})$.
    $w[h+1]$ has to be bound to $w[h-1]$ because $w[h-1]$ has bindings, that is, $w[h+1]$ consumes at least one hand and supplies at most one hand so that $\#bc(C_{h}) \geq \#bc(C_{h+1})$. Thus, in this cases $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
%     This time, let us consider either $n_4$ is occupied or not. If $n_4$ is occupied, then $w[h-1]$ has no active bindings that is this situation consumes some binding capabilities. If $n_4$ is free and $w[h+2]$ is stabilized in $n_4$, then $w[h-1]$ has to bind $w[h+2]$. Therefore, In this case, stabilization of $w[h-1..h+2]$ consumes some bindings. If $n_4$ is free and $w[h+2]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[h+2]$. Therefore, in this case consumes some bindings. Thus in this cases $\#bc(C_{h-1}) > \#bc(C_{h+2})$.

  \item[-]{$w[h-1]$ consumes one binding}\\
    In this case, $w_{h}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[h-1]$ and $w[h+1]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
  \item[-]{$w[h-1]$ consumes two bindings}\\
    In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies two bindings. Thus, in this cases $\#bc(C_{h-1}) > \#bc(C_{h+1})$.

  \end{itemize}

@@

@@

\proof%{Proof of Tunnel Troll Theorem}
Each bead in the transcript is bound either inside a tunnel or outside. If a bead is stabilized inside a tunnel, 
then it has at most one free neighbor, and hence its successor it to be stabilized there.
Moreover, if a bead is stabilized outside a tunnel, then its position is either an entrance of a tunnel or not.

Tunnel sections have three possible shapes up to symmetry : straight($S$), obtuse($O$) and acute($A$) turn (Fig. \ref{TTT_tunnel}), and we will consider each of those.

@@

Next, we consider the case of $\delta = 2, \alpha = 1$. We assume there is an index $h$ such that $S[h-1..h+1] = bbt$ or $S[h-1..h+1] = tbt$. According to Lemma~\ref{TTT_entrance_Tab}, if $w[h+1]$ is stabilized by tunnel $A$ or $B$, then $\#bc(C_{h-1}) > \#bc(C_{h})$. Also,  According to Lemma~\ref{TTT_tunnelC_lemma}, if $w[h+1]$ is stabilized by tunnel $C$, then $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
On the other hand, if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$ because of Lemma~\ref{TTT_exit}. Therefore, if there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$ or $S[i..j+1] = bt^mbt^nb \quad (m + n = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_{j})$.

@@

@@

\begin{proof}
%According to lemma\ref{TTT_a4_2b_lemma}, when $w[i]$ is stabilized, it has to use at least two bonds. Let us consider when a bead $w[i]$ which is the first bead out of $\hexagon_{w[-n+1]}^n$ is stabilized. See Fig.\ref{TTT_a4_first}. any $n_0, n_1, n_3, n_5$ is free because if some of them is occupied, $w[i]$ is not the first bead out of $\hexagon_{w[-n+1]}^n$. At least two neighbors of $w[i]$ except predecessor have to be occupied in order to bind. In this case, a point which is able to put a bead is only $n_2$. Therefore, any transcript cannot be stabilized in out of $\hexagon_{w[-n+1]}^n$. Hence oritatami system can yield only a finite structure whose size is $O(n^2)$ in $\delta =1, \alpha = 4$.
%%lemma???a=4??#bc(C_i) >= #bc(C_{i+1})? ?upper?left
seki sensei.
\end{proof}

\begin{figure}
 \centering
    \begin{tikzpicture}
	\fill[shift=(-120:1)] (0,0) circle [radius=0.1];
      \fill[shift=(180:0), blue] (0,0) circle [radius=0.05];

      \draw[dashed] (180:2) -- (0:2);
      \draw[dashed, shift=(-60:1)] (180:2.5) -- (0:1.5);
      \draw[->, blue] (-120:0.9) -- (-120:0.1);

	\node[below] at (-120:1) {$w_{[i-1]}$};
	\node[above] at (180:0) {$w_{[i]}$};
	\node[above] at (0:1) {$n_0$};

	\foreach \theta in {0,60,-60,120,180}{
   	   \draw [shift=(\theta:1)] (-0.05,-0.05) rectangle (0.05,0.05);
  	}

 	\node[above] at (60:1) {$n_1$};
	\node[below] at (-60:1) {$n_2$};
	\node[above] at (120:1) {$n_3$};
	\node[above] at (180:1) {$n_5$};

	\node at (0:2.5) {$n+1$};
	\node[shift=(-60:1)] at (0:2) {$n$};
    \end{tikzpicture}
    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
    \label{TTT_a4_first}
\end{figure}

>>>>

\begin{figure}[tb]
  \begin{center}
    \begin{tabular}{ccc}

@@

Suppose $w[i]$ were stabilized without any bond, that is, by a tunnel.
For that the two points that are a neighbor of both $w[i-1]$ and $w[i]$ must be occupied already.
In addition, at least one of the neighbors of $w[i]$ must be free because $S[i+1] = b$.
Thus, only the case to be considered is Fig.~\ref{TTT_tunnel_direction} (middle) with $n_5$ being occupied (that is, $n_4$ is free).
In this case, before $w[i]$ is stabilized, at lest three neighbors of $n_2$ were free and hence, a bead at $n_2$ was provided with one free bond and could form a bond with $w[i]$. \qed

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tb]
  \centering
    \begin{tabular}{cc}
    \centering
      \begin{minipage}{0.45\linewidth}
      \centering
        \begin{tikzpicture}
	\draw[white] (0:0) -- (120:1);
	\draw[white] (0:0) -- (-60:1);
	\draw[white] (0:0) -- (0:1);

            \fill[blue](0,0) circle [radius=0.05];
            \node[above] at (0,0) {$w[j]$};

@@

            \node[transform canvas={shift=(60:1)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
            \node[transform canvas={shift=(120:1)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
            \node[transform canvas={shift=(180:1)},above] {$w[j-1]$};

@@

            \fill[blue](0,0) circle [radius=0.05];
            \node[above] at (0,0) {$w[j]$};

@@

            \node[transform canvas={shift=(0:1)},right] {$n_0$};
            \node[transform canvas={shift=(60:1)},right] {$n_1$};
            \node[transform canvas={shift=(-60:1)},right] {$n_2$};
            \node[transform canvas={shift=(120:1)},left] {$n_3$};
            \node[transform canvas={shift=(-120:1)},left] {$n_4$};
            \node[transform canvas={shift=(180:1)},above] {$w[j-1]$};

          \node at (0,-2) {Point $n_1$ is occupied};
        \end{tikzpicture}
      \end{minipage}
    \end{tabular}
    \caption{Exit of Tunnel}
    \label{TTT_tunnel_exit}
\end{figure}

\begin{lemma}
\label{TTT_exit}
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$ and arity $\alpha =2$.
%Let $w[i]$ be a bead which is stabilized at the exit of a tunnel.
If $S[i+1..j+1] = bt^{(j-i-1)}b$ for some $i,j$ with $i \leq j-2$ and $S[j] \in \{ t_s, t_o\}$, then $\#bc(C_{j-2}) \geq \#bc(C_j)$, and hence, $\#bc(C_{i}) \geq \#bc(C_j)$.
If $i \leq j-3$, then the second inequality is strengthened as $\#bc(C_{i}) > \#bc(C_{j})$.
%if we assume $\#bc(C_{i-2}) - \#bc(C_{i-1}) = a$, then $\#bc(C_{i}) - \#bc(C_{i-1}) \leq a$.
\end{lemma}

\begin{proof}%[Lemma~ \ref{TTT_exit}]
Since the binding capability never increases inside a tunnel, we just need to consider the exit of a tunnel.
See Fig.\ref{TTT_tunnel_exit}. 
At least one of points $n_1$ or $n_2$ must be free because otherwise $w[j]$ would be inside of a tunnel, that is, $S[j+1]$ would not be $b$.

Let $m$ be the number of bonds $w[j-1]$ forms, that is, $\#bc(C_{j-2}) - \#bc(C_{j-1}) = m$.
We claim $\#bc(C_{j}) - \#bc(C_{j-1}) \leq m$.
Indeed, if both $n_1$ and $n_2$ are free (see Fig.~\ref{TTT_tunnel_exit}), the predecessor $w[j-1]$ must be bound to both beads at $n_3$ and at $n_4$ because both of them still have a free hand.
Hence, $m \geq 2$.
Since $\#bc(C_{j}) - \#bc(C_{j-1})$ is less than the arity, this difference is at most $m$.

If $n_1$ is occupied, then $n_2$ is free.
The predecessor $w[j-1]$ must be bound $n_4$.
Hence,  $m \geq 1$.
The bead $w[j]$ can increase the binding capability at most by 1 because one of its free neighbors would, $n_0$ or $n_2$, is to be occupied by the successor $w[j+1]$.
Therefore, $\#bc(C_{j}) - \#bc(C_{j-1}) \leq m$.

Thus,$\#bc(C_{j-2}) \geq \#bc(C_j)$ , and hence, $\#bc(C_{i}) \geq \#bc(C_j)$.
If $i \leq j-3$, then the second inequality is strengthened as $\#bc(C_{i}) > \#bc(C_{j})$ because $S[i+1] = b$, that is, $\#bc(C_{i}) > \#bc(C_{i+1})$ and $\#bc(C_{i+1}) \geq \#bc(C_j)$. \qed

@@

\begin{lemma}
\label{TTT_tunnelC_lemma}
Let $\Xi$ be a deterministic unary oritatami system of delay $\delta = 1$, arity $\alpha = 2$.
If $S[i+2] = t_a$, the following statements hold.
\begin{enumerate}
\item If $S[i] = b$, $\#bc(C_{i-1}) > \#bc(C_{i+2})$.
\item If $S[i] \in \{t_s, t_o \}$, $\#bc(C_{i-2}) > \#bc(C_{i+2})$.
\item If $S[i] = t_a$, $\#bc(C_{i-3}) - 2 \geq \#bc(C_{i+2})$.
\end{enumerate}
%If there are indices $i,j$ such that $S[i..j+1]$ is either $bbt^{(j-i-1)}b$ and $S[i+2] = t_a$ or $bt^\ell bt^{j-i-1-\ell}b$ for some $\ell$ and $S[i+l+2] = t_a$, then $\#bc(C_{i-1}) > \#bc(C_j)$.
\end{lemma}

@@

%\begin{proof}[Lemma~ \ref{TTT_tunnelC_lemma}]
%Let $\Xi$ be a unary oritatami system at $\delta = 1, \alpha = 2$.
%Assume $S[h..i+1] = bt^{i-h}b (h<i)$. If at least one of $w[h+1..i]$ are stabilized by tunnel $C$, then only $w[h+1]$ can use tunnel $C$ because if $w[g]$ which is one of $w[h+2..i]$, with $h+2 \leq g \leq i$ is stabilized by tunnel $C$, $C_g$ is a terminal.
%
%
%Let us consider stabilization $S[h-1..h+1] = tbt$ or $S[h-1..h+1] = bbt$ as follows. In result, $\#bc(C_{h-3}) > \#bc(C_{h+1})$. In addition according to Lemma~\ref{TTT_exit} $\#bc(C_{h+1}) \geq \#bc(C_{i})$. Thus, $\#bc(C_{h-3}) > \#bc(C_{h+1})$ and $\#bc(C_{h-3}) > \#bc(C_{i})$.
%\\
%
%\subsubsection{Case of $S[h-1..h+1] = bbt$}
%See Fig.~\ref{TTT_tunnelC_enter_usingBond}.
%If $w[h-1]$ forms one bond, then it leaves one free bond, but it is consumed by $w[h+1]$.
%In addition, $w[h]$ has to bound.
%Thus, in this cases, binding capability decreases by 1.
%If $w[h-1]$ forms two bonds, then it does not leave any bond.
%In addition, $w[h]$ has to be bound.
%Thus, in this case, even if $w[h+1]$ supplies two free bonds, binding capability decreases by 1.

@@

%\subsubsection{Case of $S[h-1..h+1] = tbt_a$}
%Fig.\ref{TTT_tunnelC_enter_usingTunnel} exhibits all the two kinds of stabilization depending on structures of tunnel C.
%
%%\item{Left of Fig.\ref{TTT_tunnelC_enter_usingTunnel}}\\
%  In this figure, Bead $n_4$ has at least one binding so that $w[h-1]$ has to bound $n_4$. Moreover, $w[h]$ has to bind to one of $n_1, n_2, n_3$ in order to stabilize deterministically. On the other hand, $w[h+1]$ can supply two bindings but has only two free neighbors. One of them is occupied by a successor. Therefore $w[h+1]$ can only bind one of $n_5, n_6$, that is, $w[h+1]$ supplies at most one binding. Thus, this case $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
%
%  These cases are divided on number of capabilities that $w[h-1]$ consumes.
%  \begin{itemize}
%  \item[-]{$w[h-1]$ does not consume any bindings}\\
%  According to Lemma~\ref{TTT_exit}, $\#bc(C_{h-3}) \geq \#bc(C_{h-1})$ because of $S[h-1] = t$.
%    $w[h]$ has to bound one of $n_1, n_2, n_3$ in order to stabilize deterministically so that  $\#bc(C_{h-1}) > \#bc(C_{h})$.
%    $w[h+1]$ has to be bound to $w[h-1]$ because $w[h-1]$ has bindings, that is, $w[h+1]$ consumes at least one hand and supplies at most one hand so that $\#bc(C_{h}) \geq \#bc(C_{h+1})$. Thus, in this cases $\#bc(C_{h-3}) > \#bc(C_{h+1})$.
%%     This time, let us consider either $n_4$ is occupied or not. If $n_4$ is occupied, then $w[h-1]$ has no active bindings that is this situation consumes some binding capabilities. If $n_4$ is free and $w[h+2]$ is stabilized in $n_4$, then $w[h-1]$ has to bind $w[h+2]$. Therefore, In this case, stabilization of $w[h-1..h+2]$ consumes some bindings. If $n_4$ is free and $w[h+2]$ is stabilized except $n_4$, then this oritatami system has to use two binding capabilities in order to bind $w[h+2]$. Therefore, in this case consumes some bindings. Thus in this cases $\#bc(C_{h-1}) > \#bc(C_{h+2})$.
%
%  \item[-]{$w[h-1]$ consumes one binding}\\
%    In this case, $w_{h}$ has to be bound one of $n_1, n_2, n_3$. In addition, $w[h-1]$ and $w[h+1]$ are not supply any bindings. Thus, in this cases consume some binding capabilities.
%  \item[-]{$w[h-1]$ consumes two bindings}\\
%    In this case, $w[h-1]$ already consumes two binding. $w[h]$ has to be bound. $w[h+1]$ supplies two bindings. Thus, in this cases $\#bc(C_{h-1}) > \#bc(C_{h+1})$.
%   
%  \end{itemize}

@@

%\end{proof}

@@

\proof{Proof of Tunnel Troll Theorem}
%Each bead in the transcript is bound either inside a tunnel or outside. If a bead is stabilized inside a tunnel, 
%then it has at most one free neighbor, and hence its successor it to be stabilized there.
%Moreover, if a bead is stabilized outside a tunnel, then its position is either an entrance of a tunnel or not.
%
%Tunnel sections have three possible shapes up to symmetry : straight($S$), obtuse($O$) and acute($A$) turn (Fig. \ref{fig:TTT_tunnel}), and we will consider each of those.

@@

Next, we consider the case of $\delta = 2, \alpha = 1$. We assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and $S[i+2] \in \{ t_s, t_o \} $.
Then, all $S[i+1..j]$ do not contain $t_o$; otherwise $S[i+1..j]$ contain $\blacksquare$.
Therefore according to Lemma~\ref{TTT_entrance_Tab}, $\#bc(C_{i-1}) > \#bc(C_{i})$ and moreover that, according to Lemma~\ref{TTT_exit}, $\#bc(C_{i}) \geq \#bc(C_{j})$.

On the other hand, we assume there are an indices $i$ ,$j$ such that $S[i+1..j+1] = bt^{(j-i-1)}b$ and $S[i+2] = t_a$.

Let us consider that $w[i]$ supplies two bonds (that is, $S[i] = t$).
If $S[i] \in \{ t_s, t_o \}$, $\#bc(C_{i-2}) \geq \#bc(C_{i})$ because of Lemma~\ref{TTT_exit}.
Therefore,

if $S[k..l] = bt^{l-k}b$, then $\#bc(C_{k-1}) \geq \#bc(C_{l})$ because of Lemma~\ref{TTT_exit}. Therefore, if there are indices $i$ and $j$ such that $S[i..j+1] = bbt^{(j-i-1)}b$ or $S[i..j+1] = bt^mbt^nb \quad (m + n = j-i-1)$, then $\#bc(C_{i-1}) > \#bc(C_{j})$.

@@

\begin{figure}[tb]
 \centering
    \begin{tikzpicture}

	\fill (0,0) circle [radius=0.1];
        \fill[blue] (60:1) circle [radius=0.05];
        \fill (0:1) circle [radius=0.1];

      \draw[dashed] (180:2) -- (0:2);
      \draw[dashed, shift=(60:1)] (180:2.5) -- (0:1.5);
      \draw[->, blue] (60:0.1) -- (60:0.9);

	\node[above] at (180:1) {$p_1$};
	\node[left] at (-120:1) {$p_2$};
	\node[left] at (-60:1) {$p_3$};
	\node[left, shift=(-120:1)] at (-60:1) {$p_3$};

	\draw (180:1) circle [radius=0.05];
	\draw (-120:1) circle [radius=0.05];
	\draw (-60:1) circle [radius=0.05];
	\draw[shift=(-120:1)] (-60:1) circle [radius=0.05];

	\node at (0:2.5) {$n$};
	\node[shift=(60:1)] at (0:2) {$n+1$};
    \end{tikzpicture}
    \caption{the first bead out of $\hexagon_{w[-n+1]}^n$}
    \label{TTT_a4_first}
\end{figure}

@@

\begin{proof}
Consider the moment when a bead $b$ is stabilized outside $\hexagon_O^n$ for the first time. 
See Fig.~\ref{TTT_a4_first}
There is only one bead available to stabilize $b$ there, which is $b_1$. 
In order for $b$ to avoid nondeterminism, hence, none of the beads around should not attract $b$.

The point $p_1$ must be empty because a bead there would have at least two free neighbors and hence is provided with a free hand. 
If there is a bead at $p_2$, $n$ must be at least 2 so that the bead is not singular. 
Since $p_1$ is empty, this bead has at least one free hand, a contradiction. 
Thus, $p_2$ must be also empty. 
In the same way, we can easily show that the point $p_3$ must not be occupied by a non-singular bead. 
Suppose $p_3 = O$. 
The point $p_4$ must not be empty; otherwise the singular bead, at $O$, would have a free hand. 
However, then a bead at $p_4$ would be provided with a free hand, a contradiction. 
\qed
\end{proof}
